\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Section formatting with more space
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{15pt}{8pt}

% Hyperlink styling
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\begin{document}

% Header with more spacing
\begin{center}
  {\Huge\bfseries Rodrigo Lopes,} {\small Experiments that accelerate revenue.}\\[6pt]
  \href{https://rodrigolopes.eu/?utm_source=resume&utm_medium=pdf}{rodrigolopes.eu} \textbar{}
  \href{mailto:contact@rodrigolopes.eu}{contact@rodrigolopes.eu} \textbar{}
  \href{https://www.linkedin.com/in/rodecalo/}{linkedin.com/in/rodecalo} \textbar{}
  +49 0172 5626057
\end{center}

\vspace{8pt}

\section*{Summary}
\begin{itemize}[leftmargin=*, label=$\bullet$, itemsep=0pt, parsep=4pt]
\item Senior Product Manager with 8+ years delivering measurable impact across product growth optimization and platform products. Proven ability to navigate complex stakeholder environments (M\&A integrations, innovation accelerators, consulting engagements) and drive outcomes through experimentation and cross-functional leadership.
\end{itemize}

\vspace{6pt}

\section*{Experience}
\vspace{4pt}

\noindent\textbf{World Food Programme}, Senior Product Manager \hfill Mar 2024 – Dec 2025, Munich
\begin{itemize}[leftmargin=*, label=$\bullet$, itemsep=4pt, parsep=0pt]
\item Led the end-to-end product lifecycle for an AI-powered voice agent, establishing data privacy guardrails and governance frameworks to ensure compliance with humanitarian standards and prevent hallucinations. Demonstrated 60\% cost efficiency potential vs. human-led outreach, informing strategic investment decision on AI delivery model expansion.

\item Defined analytics framework to measure user adoption and AI interface usability. Presented strategic recommendations to Innovation Accelerator leadership for scaling AI products across 20+ country programs, translating pilot insights into expansion priorities.

\item Contributed to internal experimentation platform enabling non-technical staff to test Machine Learning and Generative AI use cases across humanitarian operations. Supported product roadmap prioritization, use case validation, and governance framework development, helping WFP navigate responsible AI adoption while accelerating innovation.
\end{itemize}

\vspace{6pt}

\noindent\textbf{Forvia Hella}, Senior Product Manager \hfill Jul 2022 – Jan 2024, Berlin
\begin{itemize}[leftmargin=*, label=$\bullet$, itemsep=5pt, parsep=0pt]
\item Managed product roadmap for HELLA B2B e-commerce (60,000+ workshops), coordinating cross-functional teams across engineering, data, and commercial teams to integrate Faurecia product portfolio within 12-month timeline as part of FORVIA's €400M post-merger synergy program. Enabled €12M+ Year 1 cross-sell revenue through unified catalog and improved product discoverability.

\item Redesigned checkout flow and implemented Userlane digital adoption tools to improve order experience. Reduced order completion time by 35\%, increased self-service adoption by 40\%, and improved NPS by 22 points through streamlined product catalog navigation and multi-item cart optimization.
\end{itemize}

\vspace{6pt}

\noindent\textbf{Accenture Brasil}, Senior Product Manager \hfill Feb 2020 – Apr 2022, São Paulo, Brazil

\vspace{6pt}

\noindent\textit{E-Commerce Growth \& LatAm Expansion (Client: Natura \& Co):} Embedded as product manager for Brazil e-commerce optimization, then regional rollout.


\begin{itemize}[leftmargin=*, label=$\bullet$, itemsep=2pt, parsep=0pt]
\item Managed end-to-end checkout flow redesign (cart → payment → order confirmation), partnering with engineering, UX, and data analytics teams through agile sprint cycles.

\item Increased conversion rate by 45\% and reduced cart abandonment by 15\% through iterative A/B testing and UX optimization, implementing simplified checkout flows, Google Maps API address autocomplete, and expanded payment methods. Improved customer satisfaction by 16 points through mobile-optimized experience and streamlined multi-item ordering.

\item Managed 4-country LatAm rollout (Argentina, Colombia, Chile, Mexico) within 6-month timeline, coordinating country-specific teams on shared platform roadmap and prioritizing localization requirements (payments, language, regulatory compliance). Achieved 90\%+ feature parity and reduced time-to-market for subsequent launches by 35\% through standardized playbooks, enabling 40\%+ addressable market expansion.
\end{itemize}

\vspace{6pt}

\noindent\textbf{C\&A Brasil}, Senior Product Manager \hfill Mar 2018 – Jan 2020, São Paulo, Brazil
\begin{itemize}[leftmargin=*, label=$\bullet$, itemsep=5pt, parsep=0pt]
\item Joined as PM focused on e-commerce checkout optimization for C\&A Brasil. Led funnel analysis using Google Analytics and heatmaps, coordinated with engineering and UX teams through agile sprints, and increased conversion rate by 28\% and reduced cart abandonment by 18\% through mobile-optimized redesign, payment expansion, and data-driven experimentation.

\item Promoted to Senior PM after 18 months, assuming ownership of Checkout \& Payments vertical. Supported Salesforce Marketing Cloud CRM integration and WhatsApp Business API pilot for order notifications and customer service, expanding scope from checkout optimization to full customer journey.
\end{itemize}

\vspace{8pt}

\noindent\textbf{Mollis}, Founder \hfill 2016 – 2017, São Paulo, Brazil
\begin{itemize}[leftmargin=*, label=$\bullet$, itemsep=5pt, parsep=0pt]
\item Founded Mollis, a solo digital agency, building e-commerce solutions and digital products for 6-8 SMBs while completing university degree. Managed client discovery, vendor coordination, and delivery, establishing foundational product management skills.
\end{itemize}

\vspace{6pt}

\section*{Skills \& Tools}
\begin{itemize}[leftmargin=*, label=$\bullet$, itemsep=3pt, parsep=0pt]
\item \textbf{Product:} Product Strategy, Experimentation Frameworks, Discovery Methods, Roadmap Prioritization, OKRs, Stakeholder Alignment, Go-to-Market Planning
\item \textbf{Analytics:} SQL, A/B Testing, GA4, Mixpanel, Power BI, Tableau
\item \textbf{Tools:} Jira, Linear, Productboard, Notion, Zapier, n8n, Retool, Granola
\item \textbf{Rapid Prototyping \& Automation:} Figma, Claude Code, Codex, Gemini, VS Code, Supabase, Kilo Code
\item \textbf{AI \& ML:} ChatGPT/Claude/NotebookLM (ideation, planning, specs, research synthesis), Voice AI (Speech-to-Text, Text-to-Speech, NLP), Machine Learning Training and Use Cases Validation
\item \textbf{Platforms \& APIs:} REST APIs, Third-Party Integrations (Google Maps, WhatsApp Business, Payment Gateways), IVR Voice Platforms, VTEX E-commerce
\end{itemize}

\vspace{6pt}

\section*{Certifications}
\begin{itemize}[leftmargin=*, label=$\bullet$, itemsep=2pt, parsep=0pt]
\item 2021 – Certified Scrum Product Owner®, Scrum Alliance
\item 2020 – Enterprise Design Thinking: Team Essentials for AI, IBM
\item 2020 – Design Sprint Masterclass, AJ\&Smart
\item 2019 – Blockchain Essentials, IBM
\end{itemize}

\vspace{8pt}

\section*{Languages}
\begin{itemize}[leftmargin=*, label=$\bullet$, itemsep=2pt, parsep=0pt]
\item Portuguese (Native) \quad | \quad English (C2) \quad | \quad Spanish (C1) \quad | \quad German (B2)
\end{itemize}

\vspace{8pt}

\section*{Education}
\begin{itemize}[leftmargin=*, label=$\bullet$, itemsep=2pt, parsep=0pt]
\item 2017 – Bachelor's Degree, Business Administration and Management, USP – Universidade de São Paulo
\end{itemize}

\end{document}
